---
title: "Hello World"
author: "Longguang Qin"
date: "2015Äê12ÔÂ3ÈÕ"
output: html_document
---

This is my first R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(mtcars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(mtcars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Data

The `atmos` data set resides in the `nasaweather` package of the *R* programming language. It contains a collection of atmospheric variables measured between 1995 and 2000 on a grid of 576 coordinates in the western hemisphere. The data set comes from the [2006 ASA Data Expo](http://stat-computing.org/dataexpo/2006/).

Some of the variables in the `atmos` data set are:

* **temp** - The mean monthly air temperature near the surface of the Earth (measured in degrees kelvin (*K*))

* **pressure** - The mean monthly air pressure at the surface of the Earth (measured in millibars (*mb*))

* **ozone** - The mean monthly abundance of atmospheric ozone (measured in Dobson units (*DU*))

You can convert the temperature unit from Kelvin to Celsius with the formula

$$ celsius = kelvin - 273.15 $$

And you can convert the result to Fahrenheit with the formula

$$ fahrenheit = celsius \times \frac{5}{9} + 32 $$